---
title: "R_Worksheet_cabia#1"
author: "billy"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.
```{r}
age=c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)
```

a.
```{r}
length(age)

```


b.
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,51, 35, 24, 33, 41)

length(age)
output: 34

# 2.
```{r}
reciprocal <- 1/age
print (reciprocal)
```

# 3.
```{r}
new_age <- c (age, 0, age)
print(new_age)
```
# The values of new_age has the same values with the age.

# 4.
```{r}
sort(age)
```

# 5.
```{r}
min(age)
max(age)
```

# 6.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
```

a.
```{r}
length(data)
```

b.

data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,2.3, 2.5, 2.3, 2.4, 2.7)

length(data)
output: 12

# 7.
```{r}
new_vector <- data
data * 2
```

# The values of data doubled

# 8.
8.1
```{r}
a <- seq(1:100)
print(a)
```
8.2
```{r}
b <- seq(20,60)
print(b)
```
8.3
```{r}
c <- mean(20,60)
print(c)
```
8.4
```{r}
d <- sum(51,91)
print(d)
```
8.5
```{r}
e <- seq(1:1000)
print(e)
```

a. 
```{r}
length1 <- length(a)
length2 <- length(b)
length3 <- length(c)
length4 <- length(d)
sum(length1+length2+length3+length4)
```

b.
8.1 a <- seq(1:100)
8.2 b <- seq(20,60)
8.3 c <- mean(20,60)
8.4 d <- sum(51,91)

 output 8.1 : 
# Prints numbers 1-100

# output 8.2:
# Prints numbers 20-60

# output 8.3:
# 20

# output 8.4:
# 142

# output 4.5:
# Prints the number 1-100
 
c. 
```{r}
max(e[e <- 10])
```
 
# 9.
```{r}
Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))
```
 
# 10.
```{r}
backwards <- seq(100,1)
print(backwards)
```

# 11.
```{r}
naturalnum <- 1:24 
multiples <- naturalnum [naturalnum %% 3 == 0 | naturalnum %% 5 == 0]
print(multiples)
sum_multiples <- sum(multiples)
print(sum_multiples)
```
 
a.
```{r}
length(backwards) + length(multiples) + length(sum_multiples)
```
 
b.
```{r}
backwards <-seq(100,1)
print(backwards)
```
 
```{r}
naturalnum <- 1:24 
multiples <- naturalnum [naturalnum %% 3 == 0 | naturalnum %% 5 == 0]
print(multiples)
sum_multiples <- sum(multiples)
print(sum_multiples)
```

# 12.
```{r}
#x <- {0 + x + 5}
```
# It is incomplete so it caused an error.
 
 
# 13.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
score[2]
score[3]
```
 
# 14.
```{r}
a = c(1, 2, NA, 4, NA, 6, 7)
print(a, na.print="-999")
```
# It displayed the vector a with NA values shown as -999 while the actual vector is unchanged with NA values.
 
 
# 15.
```{r}
name <- readline(prompt="Input your name: ")
age <- readline(prompt="Input your age: ")
print(paste("My name is", name, "and I am",age , "years old."))
print(R.version.string)
```
 
# Its output is a message with the username and age followed by the R version string 
# "My name is "name" and I am "age" years old." and "R version 4.3.1 (2024-06-01)".