---
title: "RWorksheet_cabia#4c.Rmd"
author: "Billy Brendan Cabia"
date: "2024-11-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.
# a.
```{r}
mpg_data <- read.csv("mpg.csv")

```
# b.
```{r}
str(mpg_data)
```
The categorical variables are manufacturer, model, trans, drv, fl, and class.

# c.
The continous variables are displ, year, cyl, cty, and hwy.

# 2.
```{r}
library(dplyr)
library(ggplot2)

manufacturer_count <- mpg %>%
  group_by(manufacturer) %>%
  summarise(num_models = n_distinct(model)) %>%
  arrange(desc(num_models))

manufacturer_count[1, ]

model_count <- mpg %>%
  group_by(model) %>%
  summarise(num_variations = n()) %>%
  arrange(desc(num_variations))

model_count[1, ]
```

# a.
```{r}
unique_models <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models_count = n_distinct(model))

unique_models
```
# b.
```{r}
barplot(
  unique_models$unique_models_count,
  names.arg = unique_models$manufacturer,
  las = 2,                    # Make x-axis labels vertical for better readability
  col = "lightblue",
  main = "Number of Unique Models by Manufacturer",
  xlab = "Manufacturer",
  ylab = "Unique Models Count"
)

ggplot(unique_models, aes(x = reorder(manufacturer, -unique_models_count), y = unique_models_count)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Number of Unique Models by Manufacturer", x = "Manufacturer", y = "Unique Models Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# 2.

# a.
```{r}
mpg_summary <- mpg %>%
  group_by(manufacturer, model) %>%
  summarise(count = n()) %>%
  ungroup()

ggplot(mpg_summary, aes(x = reorder(model, count), y = manufacturer)) +
  geom_point(aes(size = count, color = count)) +
  labs(title = "Relationship between Model and Manufacturer with Frequency",
       x = "Model",
       y = "Manufacturer",
       size = "Frequency",
       color = "Frequency") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# b.
The chart is hard to understand. The sizes don’t match well with the legend, and some points overlap, making it confusing. You could fix this by adding numbers to the y-axis and using `geom_jitter()` to spread out the points so they’re easier to see.
# 3.
```{r}
top_20_mpg <- head(mpg, 20)

ggplot(top_20_mpg, aes(x = reorder(model, -year), y = year)) +
  geom_point(aes(color = class), size = 3) +  # Use points colored by class
  labs(title = "Model vs Year for Top 20 Vehicles in mpg Dataset",
       x = "Model",
       y = "Year") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# 4. 
```{r}
car_counts <- mpg_data %>%
  group_by(model) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```
# a.
```{r}
top_20 <- head(car_counts, 20)

ggplot(top_20, aes(x = reorder(model, count), y = count, fill = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 20 Car Models by Count",
       x = "Car Model",
       y = "Number of Cars") +
  scale_fill_gradient(low = "green", high = "red") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# b.
```{r}
ggplot(top_20, aes(x = reorder(model, count), y = count, fill = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 20 Car Models by Count (Horizontal)",
       x = "Number of Cars",
       y = "Car Model") +
  scale_fill_gradient(low = "green", high = "red") +  # Color gradient
  theme_minimal() +
  coord_flip()
```

# 5.
```{r}
ggplot(mpg_data, aes(x = cyl, y = displ, color = displ)) +
  geom_point(size = 3, alpha = 0.7) +  # Adjust point size and transparency
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement (L)") +
  scale_color_gradient(low = "green", high = "red") + 
  theme_minimal()
```
# a. 
The more number of cylinders the higher the displacement. It shows a positive relationship.

# 6. 
```{r}
ggplot(mpg_data, aes(x = displ, y = hwy, color = cty)) +
  geom_point(size = 3, alpha = 0.7) + 
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (L)",
       y = "Highway Miles per Gallon (MPG)") +
  scale_color_gradient(low = "green", high = "red") +
  theme_minimal()
```

# 6. 
```{r}
traffic_data <- read.csv("traffic.csv")

```
# a. 
```{r}
length(traffic_data)

variable_names <- names(traffic_data)

variable_names
```
# b. 
```{r}
unique_junctions <- unique(traffic_data$Junction)

junctions_dataframes <- list()

for (junction in unique_junctions) {
  junctions_dataframes[[junction]] <- traffic_data %>%
    filter(Junction == junction)
}

head(junctions_dataframes[[1]])
```

# c. 
```{r}
ggplot(traffic_data, aes(x = DateTime, y = Vehicles, color = Junction)) +
  geom_line() +
  labs(title = "Traffic Count by Junction",
       x = "Date and Time",
       y = "Number of Vehicles") +
  theme_minimal() +
  theme(legend.position = "right") 
```
# 7. 
```{r}
library(readxl)

alexa_data <- read_excel("alexa_file.xlsx")
```
# a. 
```{r}
num_observations <- nrow(alexa_data)

num_columns <- ncol(alexa_data)

num_observations
num_columns
```
# b. 
```{r}
alexa_data$rating <- as.numeric(as.character(alexa_data$rating))
alexa_data$verified_reviews <- as.numeric(as.character(alexa_data$verified_reviews))

sum(is.na(alexa_data$rating))  
sum(is.na(alexa_data$verified_reviews)) 

variation_totals <- alexa_data %>%
  group_by(variation) %>%  
  summarize(Total_Rating = sum(rating, na.rm = TRUE),  
            Total_Verified_Reviews = sum(verified_reviews, na.rm = TRUE))

print(variation_totals)
```
# c. 
```{r}
ggplot(variation_totals, aes(x = variation, y = Total_Rating)) +
  geom_bar(stat = "identity", fill = "orange") +
  labs(title = "Total Rating by Variation",
       x = "Variation",
       y = "Total Rating") +
  theme_minimal()
```
The graph shows that each bar corresponds to the total rating for a specific variation. Although the names on the x axis overlaps.
# d. 
reviews_by_date <- alexa_data %>%
  group_by(date) %>%  # Group by date
  summarize(Total_Verified_Reviews = n())

ggplot(reviews_by_date, aes(x = date, y = Total_Verified_Reviews)) +
  geom_line(color = "blue") +  
  labs(title = "Total Verified Reviews Over Time", x = "Date", y = "Total Verified Reviews") +
  theme_minimal()  
```

# e. 
```{r}
average_ratings <- alexa_data %>%
  group_by(variation) %>%  
  summarize(Average_Rating = mean(rating, na.rm = TRUE)) 

highest_rating_variation <- average_ratings %>%
  filter(Average_Rating == max(Average_Rating)) 

ggplot(average_ratings, aes(x = reorder(variation, -Average_Rating), y = Average_Rating)) +
  geom_bar(stat = "identity", fill = "lightblue") +  
  labs(title = "Average Ratings by Variation",
       x = "Variation",
       y = "Average Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```