---
title: "RWorksheet_Cabia#2.R"
author: "Billy Brendan Cabia"
date: "2024-09-25"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.
# a.
```{r}
operator <- c(-5:5)
print(operator)
```
## It prints the values -5 to 5.

# b.
```{r}
x <- 1:7
print(x)
```
## The values of x are 1 2 3 4 5 6 7

# 2. 
```{r}
seqA <- seq(1, 3, by=0.2)
print(seqA)
```
## It's values starts from 1.0 and it increments by 0.2

# 3.
# A factory has a census of its workers. There are 50 workers in total. The following
# list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
# 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
# 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
# 18.
## a.
## 22

## b.
## 28, 36

## c.
##  

```{r}

```

# 4.
```{r}
names <- c("first"=3, "second"=0, "third"=9)
print(names)

names[c("first", "third")]
```
## It printed only the first and third and their values. 

# 5. 

```{r}
seqB <- seq(-3:2)
```

## a.
```{r}
seqB[2] <- 0
print(seqB)
```
## It changed the value of the second index to zero

# 6. 
## a. 
```{r}
months <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

dataA <- data.frame(Month = months, 
Price_per_Liter = price_per_liter, 
Purchase_Quantity = purchase_quantity)

print(dataA)
```

# b. 

```{r}
expenditure <- price_per_liter * purchase_quantity

average_expenditure <- weighted.mean(expenditure, purchase_quantity)

print(average_expenditure)

```

# 7.

## a.
```{r}
rivers


stats_vector <- c(length(rivers),
                  sum(rivers), 
                  mean(rivers), 
                  median(rivers), 
                  var(rivers), 
                  sd(rivers), 
                  min(rivers), 
                  max(rivers))

```

## b. 
## It shows the data of the built in rivers data set but the data has been altered since there are functions that are applied.

## c.
```{r}
rivers


stats_vector <- c(length(rivers),
                  sum(rivers), 
                  mean(rivers), 
                  median(rivers), 
                  var(rivers), 
                  sd(rivers), 
                  min(rivers), 
                  max(rivers))

print(stats_vector)
``` 

# 8. 
## a.

```{r}
celebrity <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", " Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling", "Brad Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
celebrity_data <- data.frame(Celebrity = celebrity, Pay = pay, Power_ranking = power_ranking)
print(celebrity_data)
```

## b.
```{r}
power_ranking[19] <- 15 
pay[19] <- 90
celebrity_data <- data.frame(Celebrity = celebrity, Pay = pay, Power_ranking = power_ranking)
print(celebrity_data)
```

## c. 
```{r}
write.csv(celebrity_data, file = "PowerRanking.csv", row.names = FALSE)
celebrity_data_imported <- read.csv("PowerRanking.csv")
celebrity_data_imported
```

## d.
```{r}
ranks <- celebrity_data[10:20,]
save(ranks, file = "Ranks.RData")
print(ranks)
```

## e. 
# The output from the `print(selected_rows)` command will display a subset of the original data frame, specifically rows 10 to 20. This will show the names, power rankings, and annual salaries of those celebrities, to focus on particular high-ranking individuals from the list.

# 9. 
## a.
```{r}
library(readxl)
hotels_data <- read_excel("hotels-vienna.xlsx")
hotels_data
```
## b.

```{r}
dataset_dimensions <- dim(hotels_data)
dataset_dimensions
```

## c.

```{r}
library(dplyr)
selected_columns <- hotels_data %>% select(country, neighbourhood, price, stars, accommodation_type, rating)
selected_columns
```

## d.

```{r}
library(readxl)
library(dplyr)

hotels_data <- read_excel("hotels-vienna.xlsx")
colnames(hotels_data)
selected_columns <- hotels_data %>% select(country, neighbourhood, price, stars, accommodation_type, rating)
save(selected_columns, file = "new.RData")
```

## e.

```{r}
load("new.RData")

first_six_rows <- head(selected_columns)
print(first_six_rows)

last_six_rows <- tail(selected_columns)
print(last_six_rows)
```

# 10.
## a.
```{r}
vegetables <- c("squash", "okra", "carrot", "potato", "cabbage", "radish", "lettuce", "broccoli", "mushroom", "eggplant")
print(vegetables)
```
## b.
```{r}
vegetables <- c(vegetables, "garlic","ginger")
print(vegetables)
```
## c.
```{r}
vegetables <- append(vegetables, c("beans", "lemongrass", "leek", "cilantro"), after = 5)
print(vegetables)
length(vegetables)
```
## d.
```{r}
vegetables <- vegetables[-c(5, 10, 15)]
print(vegetables)
length(vegetables)
```