---
title: "RWorksheet_cabia#3b"
author: "Billy Brendan Cabia"
date: "2024-10-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1.
# a.
```{r}
dframe <- data.frame(
  Respondents = 1:20, 
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1), 
  Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6), 
  SiblingsatSchool = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2), 
  typesofHouses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
  )

dframe
```
# b.
```{r}
str(dframe)
```
# The structure displays the number of rows and columns in the data frame. It provides a preview of the first few entries and shows the data type of each column.
# c.
```{r}
mean(dframe$SiblingsatSchool)
```
# d.
```{r}
subset<- dframe[1:2, ]
subset 
```
# e.
```{r}
subset <- dframe[c(3, 5), c(2, 4)]
subset
```
# f.
```{r}
types_houses <- dframe$typesofHouses
```
# g.
```{r}
maleF <- subset(dframe, Sex == 1 & Fathers_Occupation == 1)
maleF
```
# h.
```{r}
femaleS <- subset(dframe, Sex == 2 & SiblingsatSchool >= 5)
femaleS
```

# 2.
# a.
```{r}
df = data.frame(Ints=integer(),
          Doubles=double(), Characters=character(),
          Logicals=logical(),
          Factors=factor(),
          stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
# The code creates an empty data frame with five columns of different data types.

# 3.
# a.
```{r}
householddata <- data.frame(
  Respondents = 1:10,
  Sex = c("Male", "Female", "Female", "Male", "Male", "Female", "Female", "Male", "Female", "Male"),
  Fathers_Occupation = c(1, 2, 3, 3, 1, 2, 2, 1, 1, 3),
  Persons_at_Home = c(5, 7, 3, 8, 6, 4, 2, 4, 11, 6),
  Siblings_at_School = c(5, 3, 3, 5, 6, 3, 1, 2, 6, 6),
  Types_of_Houses = c("Wood", "Concrete", "Concrete", "Wood", "Semi-concrete", "Semi-concrete", "Wood", "Semi-concrete", "Semi-concrete", "Concrete")
)
householddata

write.csv(householddata, file = "HouseholdData.csv", row.names = FALSE)

householddata <- read.csv("HouseholdData.csv")

householddata
```
# b.
```{r}
householddata$Sex <- factor(householddata$Sex, levels = c("Male", "Female"), labels = c(1, 2))

householddata$Sex <- as.integer(householddata$Sex)
householddata
```
# c.
```{r}
householddata$Types_of_Houses <- factor(householddata$Types_of_Houses, levels = c("Wood", "Concrete", "Semi-concrete"), labels = c(1, 2, 3))

householddata$Types_of_Houses <- as.integer(householddata$Types_of_Houses)

householddata
```
# d.
```{r}
householddata$Fathers_Occupation <- factor(householddata$Fathers_Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))

householddata$Fathers_Occupation <- as.integer(householddata$Fathers_Occupation)

householddata
```
# e.
```{r}
female_driver_respondents <- subset(householddata, Sex == 2 & Fathers_Occupation == 2)
female_driver_respondents
```
# f.
```{r}
siblings <- subset(householddata, Siblings_at_School >= 5)
siblings

```

# 4.
# The bar graph shows the sentiment analysis of tweets over a period of days, it shows how the volume of tweets with positive, neutral, and negative sentiments varied daily. 
